---
title: "Crowdedness at the Campus Gym"
author: "Justin Dong, David Pham"
date: "1/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(installr)
library(ggplot2)
library(knitr)
gym_data <- read.csv("../data/data.csv")
source("../source/table.R")
source("../source/chart_1.R")
source("../source/chart_3.R")
source("../source/summary.R")
```

## About Our Data
Our data set, "Crowdedness at the Campus Gym," contains `r get_observations()` observations total with `r get_metrics()` variables that were measured about different traffic levels at the Berkeley campus gym. The most amount of people inside the gym is `r get_max_crowdedness()` while the average amount of people present at the gym is `r get_average_crowdedness()`. The average temperature of the location of the gym is `r get_average_temperature()`, which is much higher than Seattles.

## Table
```{r}
kable(sorted[1:50, ], caption = "Aggregate Information Table")
```

The table shows a summary of the gym data under certain conditions. It removes uncessary columns that we are not calculating yet, and combines
and takes use of the columns we are looking at as of right now like whether its a weekend or holiday. It also filters the data to only takes
data from times that are above 60 degreees. This then shows the temperatures in descending order so we have the highest temperature peaks at the top.
This table shows us how frequent people go to the gym during peak hours of temperatures. This could help us see if theres any correlation
between temperature and how busy the gym is for college age students.

```{r heatmap, echo = FALSE}
plot(average_people_chart)
```

This chart shows a heat mapping of every weekday and the average amount of people you can expect in the gym at any time. This can show us how busy
individual days at the gym and find out what days have the least amount of people. This can help people optimize what days they want to go the gym if
they are trying to avoid the most amount of people. The heatmap shows each individual day and a red to orange assortment to show how busy the
it is for that day.

```{r scatterplot, echo = FALSE}
plot(temp_variance_plot)
```

This scatterplot compares the difference in temperature from the average and then shows the amount of people at the gym during that time. This includes
a trend line to show the times with the most frequent people. This focus more on the difference in temperature from the average rather than just a general
temperature against gym crowdedness. This can help compare how lower or higher temperatures affects how busy the gym is.

```{r scatterplot, echo = FALSE}
plot(scatterplot)
```

This scatterplot shows a plot of number of people at the gym compared to temperature. It can show us how frequent people visit the gym at each temperature
range. The busiest parts of the scatterplot start to show a density by color to properly show how busy it is. This can help determine what times
are best to go the gym for groups of people that are trying to avoid people or just to let people know how busy the gym could be. The scatterplot
shows black dots for each point but as a area gets really busy, it switches to a graident of yellow to gold to show busy the gym is.
